---
title: "Does Town Size Influence Youth Employment Opportunities?"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Does Town Size Influence Youth Employment Opportunities?}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include=FALSE}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(kableExtra)
library(broom)
```

The common perception that moving to a large city automatically leads to better job opportunities has been widely accepted for years. However, this analysis seeks to question that assumption by exploring whether 19-year-olds have better employment opportunities in smaller towns compared to bigger cities. Understanding this dynamic could offer valuable insights for young adults in the early stages of their career planning.

```{r, include=FALSE}
load("D:/SEM_2/ETC5523 CWD/Assignments/Assignment 4/assignment-4-packages-and-shiny-apps-ArunPrakash2901/data/ukTownData.rda")
```

```{r}
ukTownData1 <- ukTownData |>
  filter(earnings_above_0_at_19 != "*") |>
  mutate(Employment_Rate = as.numeric(earnings_above_0_at_19), 
         Size_Classification = as.factor(size)) |>
  filter(!Size_Classification %in% c("Inner London BUA", "Outer london BUA", "Not BUA", "Other Small BUAs"))
```

The box plot below (@fig-boxplot) illustrates the distribution of employment rates across different town sizes. Small towns demonstrate a higher median employment rate for 19-year-olds compared to cities, which show both the lowest median and the largest variation in employment outcomes.

```{r}
#| label: fig-boxplot
#| fig-cap: "The distribution of employment rates at age 19 across different town sizes. Cities have the lowest median and largest variation, while Small Towns have the highest variation but a median similar to Medium and Large Towns."
ggplot(ukTownData1, aes(x = Size_Classification, y = Employment_Rate)) +
  geom_boxplot(fill = "steelblue") +
  labs(title = "Employment Rate Distribution at Age 19 by Town Size",
       x = "Town Size Classification",
       y = "Employment Rate (%)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

To quantify the employment opportunities in each town size, the table below (@tbl-employment-rate) summarizes the average employment rates for each category. Small towns lead with an average employment rate of 50.1%, while cities fall behind with 42.6%.

```{r}
#| label: tbl-employment-rate
#| tbl-cap: "The average employment rates for 19-year-olds across different town sizes. Small towns exhibit the highest average employment rates, while cities show the lowest."
employment_summary <- ukTownData1 |>
  group_by(Size_Classification) |>
  summarise(Average_Employment_Rate = mean(Employment_Rate, na.rm = TRUE))

kable(employment_summary) |> 
  kable_styling(font_size = 15)
```

To confirm whether these differences in employment rates across town sizes are statistically significant, an ANOVA test was conducted. The results below (@tbl-anova) indicate that there is a statistically significant difference between the town size categories.

```{r}
#| label: tbl-anova
#| tbl-cap: "ANOVA Results for the Effect of Town Size Classification on Employment Rates at Age 19"
anova_result <- aov(Employment_Rate ~ Size_Classification, data = ukTownData1)
kable(tidy(anova_result)) |> 
  kable_styling(font_size = 10)
```

While ANOVA identifies that differences exist between town sizes, it does not specify which pairs of town sizes differ significantly. The Tukey HSD post-hoc test (see table @tbl-posthoc) addresses this by providing pairwise comparisons between town sizes.

```{r, echo=FALSE}
#| label: tbl-posthoc
#| tbl-cap: "Tukey HSD Post-hoc Test results showing pairwise comparisons between town sizes. Small and Medium Towns exhibit significantly higher employment rates than Cities and Large Towns."
posthoc_result <- TukeyHSD(anova_result) |> 
  tidy() |> 
  select(-term, -null.value)

kable(posthoc_result) |> 
  kable_styling(font_size = 10) 
```

The comparison between **Large Towns vs. City** did not show a statistically significant difference (p = 0.107), suggesting relatively similar employment rates between these two categories.

The Tukey HSD results are further visualized in the plot below (@fig-HSD), highlighting the confidence intervals for each comparison. Comparisons where the confidence intervals do not cross zero indicate statistically significant differences.

```{r}
#| label: fig-HSD
#| fig.cap: "The figure provides a quick visual overview of which pairwise comparisons are significant."
tukey_hsd <- ggplot(posthoc_result, aes(x = estimate, y = reorder(contrast, estimate))) +
  geom_point(aes(color = adj.p.value < 0.05), size = 3) + 
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.2) + 
  geom_vline(xintercept = 0, linetype = "dashed", color = "red") +
  labs(x = "Mean Difference (Estimate)", y = "Contrast", title = "Tukey HSD Post-hoc Test Results") +
  theme_minimal() +
  scale_color_manual(values = c("TRUE" = "blue", "FALSE" = "black")) +
  theme(legend.position = "none")
tukey_hsd
```
